Brownian dynamics simulation of cytoplasmic dynein reproduces bidirectional stepping

### 2018-10-28 papers/paper/paper.tex
Add a bit of new work to the intro

\title{Dynein walks like an Imperial AT-ST}

@@

@@

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
\caption{}
\label{fig:}
\end{figure}

@@

\subsection{Elliott}
\begin{enumerate}
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item When we have all data, write discussion
\item Rewrite introduction
\item Possibly sample stalk angles at high resolution and also 50ms, to show why the low time resolution in Lessinger prevented them from seeing the powerstroke?
\item Test suite for paper plots to see if there aren't subtle bugs?
\end{enumerate}

>>>>

\title{Brownian dynamics simulation of cytoplasmic dynein reproduces bidirectional stepping}

@@

\textbf{New intro}\\

--Background on dynein
--Evidence for dynein's powerstroke

However, to our knowledge, no work has been done to study dynein dynamics computationally. Existing models use chemical rate transitions and assume independence of steps \cite{sarlahmodel}. No models exist which account for the diffusion dynamics or conformational changes of dynein as it walks along the microtubule. Understanding the coordinated dynamics of dynein's domains is necessary to fully describe the protein's motility. Testing whether the current powerstroke model is capable of generating processive motion would be a good first step to understanding dynein's dynamics.\\

Here we present a course-grained model of cytoplasmic dynein which treats its domains as connected rigid bodies. Chemical transitions and conformational changes consistent with the powerstroke model are accounted for via elastic forces. The dynamics are determined using Brownian dynamics. The model is capable of generating directed motility at rates similar to experiment. Further, we show that the model displays further complex behavior, such as tension gating and force-mediated bidirectionality.\\

@@

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
\caption{Gennerich et al \cite{responsetoload}}
\label{fig:}
\end{figure}

@@

\subsection{Elliott}
\begin{enumerate}
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item When we have all data, write discussion
\item Rewrite introduction
\item Possibly sample stalk angles at high resolution and also 50ms, to show why the low time resolution in Lessinger prevented them from seeing the powerstroke?
\item Test suite for paper plots to see if there aren't subtle bugs?
\item Re-run velocity vs force simulation at a much lower rate to match the Gennerich velocity at pN=0
\end{enumerate}
